\textsf{Are large language models superhuman chemists?}

### 2024-10-18 src/tex/appendix.tex

>>>>

The corpus of the questions in \chembench, as shown in \Cref{tab:chembench_corpus_topic}, can be divided according to which chemical topic they belong to.

\begin{table*}[!t]
    \centering
        \caption{Examples for each of the topics considered in the evaluation of the \chembench corpus.}
    \begin{tabular}{p{2.7cm}cp{10cm}}
        \toprule
        \textbf{Question Type} & \textbf{\%} & \textbf{Example Questions}  \\ 
        \midrule
        Chemical Preference & 35.0 & Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
        & & A. [START_SMILES]N#Cc1ccc(OCCCN2CC3CN(CCNS(=O)(=O)c4ccc(F)cc4)CC(C2)O3)cc1[END_SMILES] \\
        & & B. [START_SMILES]O=C1CC(c2ccc(CC(NS(=O)(=O)c3cc(Cl)cc(Cl)c3)c3nc4ccccc4[nH]3)cc2)S(=O)(=O)N1[END_SMILES] \\
        \midrule
        Technical Chemistry & 1.5 & Which of the following statements is true about the different types of ideal reactors? \\
        & & A. In a batch reactor, the composition is uniformly mixed and remains the same throughout the reactor and at the exit \\
        & & B. In a batch reactor, the fluid passes through the reactor with no mixing of earlier and later entering fluid \\
        & & C. In a mixed flow reactor, the composition changes with time but is uniform everywhere within the reactor \\
        & & D. In a plug flow reactor, the fluid moves in single flow through the reactor with no mixing and no overtaking \\
        \midrule
        Organic Chemistry & 15.5 & What is the reaction mechanism that describes the following reaction (represented using reaction SMILES) [START_RXNSMILES]CCCl.CO[Na]>>[Na]Cl.CCOC[END_RXNSMILES]? \\
        & & A. $E_1$ \\
        & & B. $E_{cb}$ \\
        & & C. $S_N1$ \\
        & & D. $S_N2$ \\
        \midrule
        Toxicity/Safety & 24.2 & Pindolol and propranolol are (relatively nonselective) antagonists at $\beta_1$- and $\beta_2$-adrenoceptors. However, pindolol is a partial agonist, whereas propranolol is a pure antagonist. What follows from this? \\
        & & A. Pindolol has a greater therapeutic range than propranolol \\
        & & B. Pindolol has a longer half-life than propranolol \\
        & & C. Pindolol has intrinsic activity \\
        & & D. Pindolol is more lipophilic than propranolol \\
        & & E. Pindolol is more potent than propranolol \\
        \midrule
        Analytical Chemistry & 5.8 & Which of the following analytical methods is most appropriate for performing a survey analysis of a solid sample containing various metals? \\
        & & A. X-ray fluorescence analysis \\
        & & B. Differential pulse polarography \\
        & & C. Flame-atomic absorption spectroscopy \\
        & & D. Gas chromatography with flame ionization detector \\
        & & E. Hydride generation atomic absorption spectroscopy \\
        \midrule
        Materials Science & 3.1 & For NMR analysis, you need to digest the MOF in a strong acid to remove the linker and leave the metal clusters intact. Why would one choose \\ce{HF} over \\ce{HCl} for this purpose? \\
        & & A. \\ce{F-} forms a stable bonds to the metal ions \\
        & & B. \\ce{HF} has a better water solubility than \\ce{HCl} \\
        & & C. \\ce{HF} has a higher boiling point than \\ce{HCl} \\
        & & D. \\ce{HF} is a weaker acid than \\ce{HCl} \\
        \midrule
        General Chemistry & 5.3 & Which of the following salts is an acidic salt? \\
        & & A. \\ce{NH4Cl} \\
        & & B. \\ce{Na2CO3} \\
        & & C. \\ce{NaH2PO4} \\
        & & D. \\ce{Zn(OH)Cl} \\
        \midrule
        Physical Chemistry & 6.3 & The Born-Oppenheimer (BO) approximation is widely used in computational chemistry, but its accuracy can vary depending on the system. Among the following options, for which system is the Born-Oppenheimer approximation likely to be least applicable? \\
        & & A. \\ce{C60} \\
        & & B. \\ce{CH4} \\
        & & C. \\ce{Fe(CO)5} \\
        & & D. \\ce{H2+} \\
        & & E. \\ce{NaCl} \\
        \midrule
        Inorganic Chemistry & 3.3 & What is the oxidation number of the metal in the compound \\ce{[ZrF7]^{3-}}\\
    \end{tabular}
    \label{tab:chembench_corpus_topic}
\end{table*}

In addition, as shown in \Cref{tab:chembench_corpus_cognitive} the \chembench corpus can be divided considering the different skills needed to solve the questions.

\begin{table*}[!t]
    \centering
        \caption{Examples for each of the required skills considered in the \chembench corpus.}
    \begin{tabular}{p{2.7cm}cp{10cm}}
        \toprule
        \textbf{Required skills} & \textbf{Number of Questions} & \textbf{Example Question} \\
        \midrule
        Knowledge & 770 & Which of the following salts is an acidic salt? \\
        & & A. \\ce{NH4Cl} \\
        & & B. \\ce{Na2CO3} \\
        & & C. \\ce{NaH2PO4} \\
        & & D. \\ce{Zn(OH)Cl} \\
        \midrule
        Reasoning & 825 & How can the optical impact of quantum confinement on the electronic structure of a quantum dot be observed experimentally? \\
        & & A. By measuring atomic force microscopy \\
        & & B. By measuring fourier transform infrared spectroscopy \\
        & & C. By measuring photoluminescence spectrum \\
        & & D. By measuring the absorption spectroscopy \\
        \midrule
        Intuition & 1001 & Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
        & & A. [START_SMILES]CC1(C)Oc2ccc([N+](=O)[O-])cc2[C@@H](N2CCOCC2)[C@@H]1O[END_SMILES] \\
        & & B. [START_SMILES]Cc1ccccc1N=C(S)N1CCC(NC(=O)c2ccco2)CC1[END_SMILES] \\
        \midrule
        Calculation & 91 & Given that the average molar mass of the polymer chains in this sample of poly(lactic acid) (PLA) is \\pu{595 g mol^{-1}} using end-group analysis, where \\pu{0.1619 g} of PLA was dissolved in \\pu{25 cm^3} of benzyl alcohol and titrated with \\pu{0.0400 mol dm^{-3}} \\ce{KOH} solution. The volume of \\ce{KOH} solution required to reach the endpoint was \\pu{6.81 cm^3}. What is the average number of monomer units in each polymer chain of this sample? \\
        \bottomrule
    \end{tabular}
    \label{tab:chembench_corpus_cognitive}
\end{table*}
